%% ---------------- TCPDUMP ----------------
\subsection{Enabling ordinary users to execute tcpdump}
\label{s:EnableTCPDumpNormalUsers}
tcpdump requires higher privileges to capture incoming and outgoing traffic on the network interface.
Since tcpdump is the program used for packet capturing in this research, it would be more efficient to give an ordinary user access to this program file and traffic capturing.
The design of the capture is that the scanner uses SSH to issue tasks to each worker host.
If tcpdump requires root access, this will lead to more complications in configurations on the worker host while issuing tasks to a worker.
This issue is mitigated by setting the set-user-ID bit on the tcpdump program, enabling unprivileged users to capture traffic on the worker host's network interface, which normally requires privileged access.

Since the worker hosts are located on an isolated virtual network, the risk of unauthorized access is reduced and enabling simplistic capture of packets without any advanced configuration changes.
These commands shown in listing \ref{lst:CmdChmodTcpdump} must be executed as $root$ on the worker to gain effect. The command in line one would return the full path for tcpdump, as seen in line two.
Line three changes the modifications on the program, setting the set-user-ID bit.
To assure that this is executed successfully, line four would list the permissions for the file shown inline five. Here we see that the $s$ flag is set for the owner ($-rws$) and the group ($r-s$), while a normal user has read and execution permissions ($r-x$).

\begin{listing}[!ht]
\caption{Command for changing mode on tcpdump file}
\label{lst:CmdChmodTcpdump}
\begin{minted}[linenos]{Bash}
which tcpdump
/usr/sbin/tcpdump
chmod +s /usr/sbin/tcpdump
ls -l /usr/sbin/tcpdump
-rwsr-sr-x 1 root root 1044232 Dec 31  2019 /usr/sbin/tcpdump
\end{minted}
\end{listing}

After setting the set-user-ID bit on the file, the file rights looks similar like mentioned in the listing above.

%% ---------------- /TCPDUMP ----------------