\subsection{Task manager}
\label{ss:Cleanup}

The main objective of this script is to maintain the tasklist, changing the status of tasks from ongoing to completed.
This script is executed through the terminal as a user and is not designed to run through a cronjob.
The main input to this script is the given task file.

\subsubsection{Process comparison}
This function extracts the executed command for a process matching tcpdump and pipes the output to a temporary file.
The temporary file is iterated through, and the PID for each running tcpdump is retrieved.
From here, the function compares the task name to processes initiated through SSH to each worker.
The function then checks if there is a scanning process towards the given work with the correlating task name.
If there is no PID returned from this check, the function terminates the tcpdump on the worker.

\begin{listing}[!ht]
\caption{Process comparison and TCPDump termination}
\label{lst:ProcessCompare}
\begin{minted}{Bash}
process_comparision_clean() {
  YEAR=$(date +%Y)
  ps -eo command | grep tcpdump | grep -v grep | sed 's/^ssh.*-w //g' | \
  sed "s/_$YEAR.*$//g" > ps_comparision

  while read TASK_NAME
  do
    SCANNER_PID=$(ps -eo pid,command | grep "$TASK_NAME" | grep -Ev 'tcpdump|grep' | \
    awk '{ print $1 }')
    if [[ -z $SCANNER_PID ]]; then
      terminate_tcpdump $TASK_NAME
    fi

  done < ps_comparision
}
\end{minted}
\end{listing}


\subsubsection{Reused functions from the scanner script}
\label{ss:ReusedFunctionsScannerScript}
Compared to the scanner script, functions have been reused within this script.
These are important functions for colorizing messages, checking scan status, terminating tcpdump, changing task status, and updating task list.
These functions are described within the scanner section \ref{s:ScannerScript}.


Further on, this script contains a true while loop for continuously running checks to update the tasks.
The reason behind this is to reduce the amount of irrelevant traffic generated after a scan is completed.


\begin{listing}[!ht]
\caption{Update tasklist continously}
\label{lst:TasklistUpdateContinue}
\begin{minted}{Bash}
while true
do
  if update_tasklist; then
    DATE=$(date "+%d.%m.%Y %H:%M:%S")
    printf "\r[ $DATE ] Cleaned taskfile: $TASK_FILE"
    sleep 2
  else
    printf "\r[ $DATE ] Failed cleaning taskfile: $TASK_FILE"
  fi
done
\end{minted}
\end{listing}